---
title: "Untitled"
author: "Lauren Kennedy"
date: "14/02/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}

library(tidyverse)
library(ggplot2)
library(ggthemes)
library(here)
library(viridis)

results_biasvar <- readRDS(here(paste0("results/sim_results_biasvar_",1,".rds"))) %>%
  mutate(iteration = 1)

for(iteration in c(1:64,67:74,76:79,88:90,92:198,201:296,298:500)) {
  tmp <- readRDS(here(paste0("results/sim_results_biasvar_",iteration,".rds"))) %>%
    mutate(iteration = iteration)
  results_biasvar <- rbind(tmp,results_biasvar)
}

```

### Focussing on when all genders have different E[Y]

We see that the response behaviour impacts the efficacy of using demographics.

Note that imputation error isn't included in uncertainty
```{r}

col_pal = c("#56B4E9","#009E73","#0072B2","#F0E442","#E69F00","#CC79A7")

names(col_pal)<- levels(results_biasvar$method)            
            
bias_pop = results_biasvar %>%
  mutate(cond =  factor(cond, labels = c("No gender differences","Male, female same, non-binary different","Female, non-binary same, male different", "All different"))) %>%
  filter(nb_representation =="under", cond =="All different")%>%
  select(bias_y, ci_width_y, cond, estimate,reps, prop_resp_male, nb_representation,method)%>%
  ggplot(., aes(x=method, y = bias_y, fill = method))+
  geom_hline(yintercept=0)+
  geom_boxplot()+
  facet_grid(prop_resp_male~estimate)+
  scale_fill_manual(name = "method", values = col_pal)+
  theme_bw()+
  coord_flip()+
  theme(legend.position = "none",
        legend.title = element_blank(),
        axis.title.y = element_blank())+
  ylab("Bias at estimating population mean")


ggsave("Figures/mrp_wtd_y_bias.png",bias_pop, width = 20, height = 10, units = "cm")
```


```{r}
width_pop =results_biasvar %>%
  mutate(cond =  factor(cond, labels = c("No gender differences","Male, female same, non-binary different","Female, non-binary same, male different", "All different"))) %>%
  filter(nb_representation =="under", cond =="All different")%>%
  select(bias_y, ci_width_y, cond, estimate,reps, prop_resp_male, nb_representation,method)%>%
  ggplot(., aes(x=method, y = ci_width_y, fill = method))+
  geom_boxplot()+
  facet_grid(prop_resp_male~estimate, scales = "free_x")+
  scale_fill_manual(name = "method", values = col_pal)+
  theme_bw()+
  coord_flip()+
  theme(legend.position = "none",
        legend.title = element_blank(),
        axis.title.y = element_blank())+
  ylab("Width of uncertainty")


ggsave("Figures/mrp_wtd_y_ciwidth.png",width_pop, width = 20, height = 10, units = "cm")

```

### Focussing on sex sub group estimates

Subset to when all genders have different E[Y], and prob of resp of male for nb folks is even 

```{r}
bias_sex  = results_biasvar %>%
  mutate(cond =  factor(cond, labels = c("No gender differences","Male, female same, non-binary different","Female, non-binary same, male different", "All different"))) %>%
  filter(nb_representation =="under", cond =="All different", prop_resp_male == .5)%>%
  select(bias_y_sex_f,bias_y_sex_m, cond, estimate,reps, nb_representation,method)%>%
  pivot_longer(cols = starts_with("bias_y_sex_"), 
               names_to = "sex",
               values_to = "bias_y")%>%
  mutate(sex = fct_recode(sex,"Female" = "bias_y_sex_f","Male" = "bias_y_sex_m"))%>%
  ggplot(., aes(x=method, y = bias_y, fill = method))+
  geom_hline(yintercept=0)+
  geom_boxplot()+
  facet_grid(sex~estimate)+
  scale_fill_manual(name = "method", values = col_pal)+
  theme_bw()+
  coord_flip()+
  theme(legend.position = "none",
        legend.title = element_blank(),
        axis.title.y = element_blank())+
  ylab("Bias at estimating population mean")


ggsave("Figures/mrp_wtd_sex_bias.png",bias_sex, width = 20, height = 10, units = "cm")


```

```{r}
ciwidth_sex = results_biasvar %>%
  mutate(cond =  factor(cond, labels = c("No gender differences","Male, female same, non-binary different","Female, non-binary same, male different", "All different"))) %>%
  filter(nb_representation =="under", cond =="All different", prop_resp_male == .5)%>%
  select(ci_width_y_sex_f,ci_width_y_sex_m, cond, estimate,reps, nb_representation,method)%>%
  pivot_longer(cols = starts_with("ci_width_y_sex_"), 
               names_to = "sex",
               values_to = "ci_width_y")%>%
  mutate(sex = fct_recode(sex,"Female" = "ci_width_y_sex_f","Male" = "ci_width_y_sex_m"))%>%
  ggplot(., aes(x=method, y = ci_width_y, fill = method))+
  geom_boxplot()+
  facet_grid(sex~estimate, scales = "free_x")+
  scale_fill_manual(name = "method", values = col_pal)+
  theme_bw()+
  coord_flip()+
  theme(legend.position = "none",
        legend.title = element_blank(),
        axis.title.y = element_blank())+
  ylab("CI width for population mean")


ggsave("Figures/mrp_wtd_sex_ciwidth.png",ciwidth_sex, width = 20, height = 10, units = "cm")
```


### Focussing on gender sub group estimates

Subset to when all genders have different E[Y], and prob of resp of male for nb folks is even 

```{r}
bias_gender = results_biasvar %>%
  mutate(cond =  factor(cond, labels = c("No gender differences","Male, female same, non-binary different","Female, non-binary same, male different", "All different"))) %>%
  filter(nb_representation =="under", cond =="All different", prop_resp_male == .5)%>%
  select(bias_y_gender_f,bias_y_gender_m,bias_y_gender_nb, cond, estimate,reps, nb_representation,method)%>%
  pivot_longer(cols = starts_with("bias_y_gender_"), 
               names_to = "gender",
               values_to = "bias_y")%>%
  mutate(gender = fct_recode(gender,"Female" = "bias_y_gender_f","Male" = "bias_y_gender_m","Non-binary" = "bias_y_gender_nb"))%>%
  ggplot(., aes(x=method, y = bias_y, fill = method))+
  geom_boxplot()+
  facet_grid(gender~estimate, scales = "free_x")+
  scale_fill_manual(name = "method", values = col_pal)+
  theme_bw()+
  coord_flip()+
  theme(legend.position = "none",
        legend.title = element_blank(),
        axis.title.y = element_blank())+
  ylab("Bias at estimating population mean")

ggsave("Figures/mrp_wtd_gender_bias.png",bias_gender, width = 20, height = 10, units = "cm")
```

```{r}
width_gender = results_biasvar %>%
  mutate(cond =  factor(cond, labels = c("No gender differences","Male, female same, non-binary different","Female, non-binary same, male different", "All different"))) %>%
  filter(nb_representation =="under", cond =="All different", prop_resp_male == .5)%>%
  select(ci_width_y_gender_f,ci_width_y_gender_m,ci_width_y_gender_nb, cond, estimate,reps, nb_representation,method)%>%
  pivot_longer(cols = starts_with("ci_width_y_gender_"), 
               names_to = "gender",
               values_to = "ci_width_y")%>%
  mutate(gender = fct_recode(gender,"Female" = "ci_width_y_gender_f","Male" = "ci_width_y_gender_m","Non-binary" = "ci_width_y_gender_nb"))%>%
  ggplot(., aes(x=method, y = ci_width_y, fill = method))+
  geom_boxplot()+
  facet_grid(gender~estimate, scales = "free_x")+
  scale_fill_manual(name = "method", values = col_pal)+
  theme_bw()+
  coord_flip()+
  theme(legend.position = "none",
        legend.title = element_blank(),
        axis.title.y = element_blank())+
  ylab("CI width for population mean")

ggsave("Figures/mrp_wtd_gender_width.png",width_gender, width = 20, height = 10, units = "cm")
```
