---
title: "Figures Appendix"
author: "Lauren Kennedy"
date: "11/03/2022"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r}
library(tidyverse)
library(ggplot2)
library(ggthemes)
library(here)
library(viridis)

results_biasvar <- readRDS(here(paste0("results/sim_results_biasvar_",1,".rds"))) %>%
  mutate(iteration = 1)

for(iteration in c(1:296,298:500)) {
  tmp <- readRDS(here(paste0("results/sim_results_biasvar_",iteration,".rds"))) %>%
    mutate(iteration = iteration)
  results_biasvar <- rbind(tmp,results_biasvar)
}

```

## Focussing on when all genders have different E[Y]

We see that the response behaviour impacts the efficacy of using demographics.

Note that imputation error isn't included in uncertainty

```{r}
bias_pop = results_biasvar %>%
  mutate(cond =  factor(cond, labels = c("No gender differences","Male, female same, non-binary different","Female, non-binary same, male different", "All different"))) %>%
  filter(cond =="All different")%>%
  select(bias_y, ci_width_y, cond, estimate,reps, prop_resp_male, nb_representation,method)%>%
  group_by(method, nb_representation, prop_resp_male, estimate)%>%
  summarise(mean_bias = mean(bias_y), low025 = quantile(bias_y, .025), up975 = quantile(bias_y, .975))%>%
  ggplot(., aes(x=method, y = mean_bias, ymin =low025, ymax=up975, colour = nb_representation))+
  geom_hline(yintercept=0)+
  geom_point(position = position_dodge(.5))+
  geom_errorbar(width = 0,alpha = .3, position = position_dodge(.5))+
  facet_grid(prop_resp_male~estimate)+
  ggthemes::scale_color_colorblind()+
  theme_bw()+
  coord_flip()+
  labs(colour = "Representation of non-binary individuals")+
  theme(legend.position = "bottom",,
        axis.title.y = element_blank())+
  ylab("Bias at estimating population mean")

bias_pop

ggsave("Appendix_Figures/mrp_wtd_y_bias_alldiff.png",bias_pop, width = 20, height = 10, units = "cm")
```



```{r}
            
width_pop = results_biasvar %>%
  mutate(cond =  factor(cond, labels = c("No gender differences","Male, female same, non-binary different","Female, non-binary same, male different", "All different"))) %>%
  filter(cond =="All different")%>%
  select(bias_y, ci_width_y, cond, estimate,reps, prop_resp_male, nb_representation,method)%>%
  group_by(method, nb_representation, prop_resp_male, estimate)%>%
  summarise(mean_width = mean(ci_width_y), low025 = quantile(ci_width_y, .025), up975 = quantile(ci_width_y, .975))%>%
  ggplot(., aes(x=method, y = mean_width, ymin =low025, ymax=up975, colour = nb_representation))+
  geom_point(position = position_dodge(.5))+
  geom_errorbar(width = 0,alpha = .3, position = position_dodge(.5))+
  facet_grid(prop_resp_male~estimate, scales = "free_x")+
  ggthemes::scale_color_colorblind()+
  theme_bw()+
  coord_flip()+
  labs(colour = "Representation of non-binary individuals")+
  theme(legend.position = "bottom",,
        axis.title.y = element_blank())+
  ylab("Width of uncertainty")

width_pop

ggsave("Appendix_Figures/mrp_wtd_y_width_alldiff.png",width_pop, width = 20, height = 10, units = "cm")
```

### Focussing on sex sub group estimates

Sex bias in estimates

```{r}
bias_sex = results_biasvar %>%
  mutate(cond =  factor(cond, labels = c("No gender differences","Male, female same, non-binary different","Female, non-binary same, male different", "All different"))) %>%
  filter(cond =="All different")%>%
  select(ci_width_y, cond, estimate,reps, prop_resp_male, nb_representation,method,bias_y_sex_f,bias_y_sex_m)%>%
  pivot_longer(cols = starts_with("bias_y_sex_"), 
               names_to = "sex",
               values_to = "bias_y", names_repair = "unique")%>%
  mutate(sex = fct_recode(sex,"Female" = "bias_y_sex_f","Male" = "bias_y_sex_m"))%>%
  group_by(method, nb_representation, prop_resp_male, estimate,sex)%>%
  summarise(mean_bias = mean(bias_y), low025 = quantile(bias_y, .025), up975 = quantile(bias_y, .975))%>%
  ggplot(., aes(x=method, y = mean_bias, ymin =low025, ymax=up975, colour = sex, shape = nb_representation))+
  geom_point(position = position_dodge(.8))+
  geom_errorbar(width = 0,alpha = .3, position = position_dodge(.8))+
  facet_grid(prop_resp_male~estimate, scales = "free_x")+
  scale_colour_manual(values = c("#009E73","#D55E00"))+# colours from the colorbling palette in ggthemes
  theme_bw()+
  coord_flip()+
  labs(shape = "Representation of non-binary individuals", colour = "Sex")+
  theme(legend.position = "bottom",,
        axis.title.y = element_blank())+
  ylab("Estimate Bias")

bias_sex

ggsave("Appendix_Figures/mrp_wtd_sex_bias_alldiff.png",bias_sex, width = 20, height = 10, units = "cm")

```


Sex bias in estimates

```{r}
ciwidth_sex = results_biasvar %>%
  mutate(cond =  factor(cond, labels = c("No gender differences","Male, female same, non-binary different","Female, non-binary same, male different", "All different"))) %>%
  filter(cond =="All different")%>%
  select(cond, estimate,reps, prop_resp_male, nb_representation,method,ci_width_y_sex_f,ci_width_y_sex_m)%>%
  pivot_longer(cols = starts_with("ci_width_y_sex_"), 
               names_to = "sex",
               values_to = "ciwidth_y", names_repair = "unique")%>%
  mutate(sex = fct_recode(sex,"Female" = "ci_width_y_sex_f","Male" = "ci_width_y_sex_m"))%>%
  group_by(method, nb_representation, prop_resp_male, estimate,sex)%>%
  summarise(ciwidth = mean(ciwidth_y), low025 = quantile(ciwidth_y, .025), up975 = quantile(ciwidth_y, .975))%>%
  ggplot(., aes(x=method, y = ciwidth, ymin =low025, ymax=up975, colour = sex, shape = nb_representation))+
  geom_point(position = position_dodge(.8))+
  geom_errorbar(width = 0,alpha = .3, position = position_dodge(.8))+
  facet_grid(prop_resp_male~estimate, scales = "free_x")+
  scale_colour_manual(values = c("#009E73","#D55E00"))+# colours from the colorbling palette in ggthemes
  theme_bw()+
  coord_flip()+
  labs(shape = "Representation of non-binary individuals", colour = "Sex")+
  theme(legend.position = "bottom",,
        axis.title.y = element_blank())+
  ylab("Width of uncertainty")

ciwidth_sex

ggsave("Appendix_Figures/mrp_wtd_sex_ciwidth_alldiff.png",ciwidth_sex, width = 20, height = 10, units = "cm")

```


### Focussing on gender sub group estimates

gender bias in estimates

```{r}
bias_gender = results_biasvar %>%
  mutate(cond =  factor(cond, labels = c("No gender differences","Male, female same, non-binary different","Female, non-binary same, male different", "All different"))) %>%
  filter(cond =="All different")%>%
  select(ci_width_y, cond, estimate,reps, prop_resp_male, nb_representation,method,bias_y_gender_f,bias_y_gender_m,bias_y_gender_nb)%>%
  pivot_longer(cols = starts_with("bias_y_gender_"), 
               names_to = "gender",
               values_to = "bias_y", names_repair = "unique")%>%
  mutate(gender = fct_recode(gender,"Female" = "bias_y_gender_f","Male" = "bias_y_gender_m","Non-binary" = "bias_y_gender_nb"))%>%
  group_by(method, nb_representation, prop_resp_male, estimate,gender)%>%
  summarise(mean_bias = mean(bias_y,na.rm = TRUE), low025 = quantile(bias_y, .025,na.rm = TRUE), up975 = quantile(bias_y, .975,na.rm = TRUE))%>%
  ggplot(., aes(x=method, y = mean_bias, ymin =low025, ymax=up975, colour = gender, shape = nb_representation))+
  geom_point(position = position_dodge(.9))+
  geom_errorbar(width = 0,alpha = .3, position = position_dodge(.9))+
  facet_grid(prop_resp_male~estimate, scales = "free_x")+
  scale_colour_manual(values = c("#009E73","#D55E00","#56B4E9"))+# colours from the colorbling palette in ggthemes
  theme_bw()+
  coord_flip()+
  labs(shape = "Representation of non-binary individuals", colour = "gender")+
  theme(legend.position = "bottom",,
        axis.title.y = element_blank())+
  ylab("Estimate Bias")

bias_gender

ggsave("Appendix_Figures/mrp_wtd_gender_bias_alldiff.png",bias_gender, width = 20, height = 10, units = "cm")

```


Gender interval width

```{r}
ci_width_gender = results_biasvar %>%
  mutate(cond =  factor(cond, labels = c("No gender differences","Male, female same, non-binary different","Female, non-binary same, male different", "All different"))) %>%
  filter(cond =="All different")%>%
  select( cond, estimate,reps, prop_resp_male, nb_representation,method,ci_width_y_gender_f,ci_width_y_gender_m,ci_width_y_gender_nb)%>%
  pivot_longer(cols = starts_with("ci_width_y_gender_"), 
               names_to = "gender",
               values_to = "ci_width_y", names_repair = "unique")%>%
  mutate(gender = fct_recode(gender,"Female" = "ci_width_y_gender_f","Male" = "ci_width_y_gender_m","Non-binary" = "ci_width_y_gender_nb"))%>%
  group_by(method, nb_representation, prop_resp_male, estimate,gender)%>%
  summarise(mean_ci_width = mean(ci_width_y,na.rm = TRUE), low025 = quantile(ci_width_y, .025,na.rm = TRUE), up975 = quantile(ci_width_y, .975,na.rm = TRUE))%>%
  ggplot(., aes(x=method, y = mean_ci_width, ymin =low025, ymax=up975, colour = gender, shape = nb_representation))+
  geom_point(position = position_dodge(.9))+
  geom_errorbar(width = 0,alpha = .3, position = position_dodge(.9))+
  facet_grid(prop_resp_male~estimate, scales = "free_x")+
  scale_colour_manual(values = c("#009E73","#D55E00","#56B4E9"))+# colours from the colorbling palette in ggthemes
  theme_bw()+
  coord_flip()+
  labs(shape = "Representation of non-binary individuals", colour = "gender")+
  theme(legend.position = "bottom",,
        axis.title.y = element_blank())+
  ylab("Estimate ci_width")

ci_width_gender

ggsave("Appendix_Figures/mrp_wtd_gender_ci_width_alldiff.png",ci_width_gender, width = 20, height = 10, units = "cm")

```



### Focussing on when all genders have same E[Y]

We see that the response behaviour impacts the efficacy of using demographics.

Note that imputation error isn't included in uncertainty

```{r}
bias_pop = results_biasvar %>%
  mutate(cond =  factor(cond, labels = c("No gender differences","Male, female same, non-binary different","Female, non-binary same, male different", "All different"))) %>%
  filter(cond =="No gender differences")%>%
  select(bias_y, ci_width_y, cond, estimate,reps, prop_resp_male, nb_representation,method)%>%
  group_by(method, nb_representation, prop_resp_male, estimate)%>%
  summarise(mean_bias = mean(bias_y), low025 = quantile(bias_y, .025), up975 = quantile(bias_y, .975))%>%
  ggplot(., aes(x=method, y = mean_bias, ymin =low025, ymax=up975, colour = nb_representation))+
  geom_hline(yintercept=0)+
  geom_point(position = position_dodge(.5))+
  geom_errorbar(width = 0,alpha = .3, position = position_dodge(.5))+
  facet_grid(prop_resp_male~estimate)+
  ggthemes::scale_color_colorblind()+
  theme_bw()+
  coord_flip()+
  labs(colour = "Representation of non-binary individuals")+
  theme(legend.position = "bottom",,
        axis.title.y = element_blank())+
  ylab("Bias at estimating population mean")

bias_pop

ggsave("Appendix_Figures/mrp_wtd_y_bias_nodiff.png",bias_pop, width = 20, height = 10, units = "cm")
```



```{r}
            
width_pop = results_biasvar %>%
  mutate(cond =  factor(cond, labels = c("No gender differences","Male, female same, non-binary different","Female, non-binary same, male different", "All different"))) %>%
  filter(cond =="No gender differences")%>%
  select(bias_y, ci_width_y, cond, estimate,reps, prop_resp_male, nb_representation,method)%>%
  group_by(method, nb_representation, prop_resp_male, estimate)%>%
  summarise(mean_width = mean(ci_width_y), low025 = quantile(ci_width_y, .025), up975 = quantile(ci_width_y, .975))%>%
  ggplot(., aes(x=method, y = mean_width, ymin =low025, ymax=up975, colour = nb_representation))+
  geom_point(position = position_dodge(.5))+
  geom_errorbar(width = 0,alpha = .3, position = position_dodge(.5))+
  facet_grid(prop_resp_male~estimate, scales = "free_x")+
  ggthemes::scale_color_colorblind()+
  theme_bw()+
  coord_flip()+
  labs(colour = "Representation of non-binary individuals")+
  theme(legend.position = "bottom",,
        axis.title.y = element_blank())+
  ylab("Width of uncertainty")

width_pop

ggsave("Appendix_Figures/mrp_wtd_y_width_nodiff.png",width_pop, width = 20, height = 10, units = "cm")
```

### Focussing on sex sub group estimates

Sex bias in estimates

```{r}
bias_sex = results_biasvar %>%
  mutate(cond =  factor(cond, labels = c("No gender differences","Male, female same, non-binary different","Female, non-binary same, male different", "All different"))) %>%
  filter(cond =="No gender differences")%>%
  select(ci_width_y, cond, estimate,reps, prop_resp_male, nb_representation,method,bias_y_sex_f,bias_y_sex_m)%>%
  pivot_longer(cols = starts_with("bias_y_sex_"), 
               names_to = "sex",
               values_to = "bias_y", names_repair = "unique")%>%
  mutate(sex = fct_recode(sex,"Female" = "bias_y_sex_f","Male" = "bias_y_sex_m"))%>%
  group_by(method, nb_representation, prop_resp_male, estimate,sex)%>%
  summarise(mean_bias = mean(bias_y), low025 = quantile(bias_y, .025), up975 = quantile(bias_y, .975))%>%
  ggplot(., aes(x=method, y = mean_bias, ymin =low025, ymax=up975, colour = sex, shape = nb_representation))+
  geom_point(position = position_dodge(.8))+
  geom_errorbar(width = 0,alpha = .3, position = position_dodge(.8))+
  facet_grid(prop_resp_male~estimate, scales = "free_x")+
  scale_colour_manual(values = c("#009E73","#D55E00"))+# colours from the colorbling palette in ggthemes
  theme_bw()+
  coord_flip()+
  labs(shape = "Representation of non-binary individuals", colour = "Sex")+
  theme(legend.position = "bottom",,
        axis.title.y = element_blank())+
  ylab("Estimate Bias")

bias_sex

ggsave("Appendix_Figures/mrp_wtd_sex_bias_nodiff.png",bias_sex, width = 20, height = 10, units = "cm")

```


Sex bias in estimates

```{r}
ciwidth_sex = results_biasvar %>%
  mutate(cond =  factor(cond, labels = c("No gender differences","Male, female same, non-binary different","Female, non-binary same, male different", "All different"))) %>%
  filter(cond =="No gender differences")%>%
  select(cond, estimate,reps, prop_resp_male, nb_representation,method,ci_width_y_sex_f,ci_width_y_sex_m)%>%
  pivot_longer(cols = starts_with("ci_width_y_sex_"), 
               names_to = "sex",
               values_to = "ciwidth_y", names_repair = "unique")%>%
  mutate(sex = fct_recode(sex,"Female" = "ci_width_y_sex_f","Male" = "ci_width_y_sex_m"))%>%
  group_by(method, nb_representation, prop_resp_male, estimate,sex)%>%
  summarise(ciwidth = mean(ciwidth_y), low025 = quantile(ciwidth_y, .025), up975 = quantile(ciwidth_y, .975))%>%
  ggplot(., aes(x=method, y = ciwidth, ymin =low025, ymax=up975, colour = sex, shape = nb_representation))+
  geom_point(position = position_dodge(.8))+
  geom_errorbar(width = 0,alpha = .3, position = position_dodge(.8))+
  facet_grid(prop_resp_male~estimate, scales = "free_x")+
  scale_colour_manual(values = c("#009E73","#D55E00"))+# colours from the colorbling palette in ggthemes
  theme_bw()+
  coord_flip()+
  labs(shape = "Representation of non-binary individuals", colour = "Sex")+
  theme(legend.position = "bottom",,
        axis.title.y = element_blank())+
  ylab("Width of uncertainty")

ciwidth_sex

ggsave("Appendix_Figures/mrp_wtd_sex_ciwidth_nodiff.png",ciwidth_sex, width = 20, height = 10, units = "cm")

```


### Focussing on gender sub group estimates

gender bias in estimates

```{r}
bias_gender = results_biasvar %>%
  mutate(cond =  factor(cond, labels = c("No gender differences","Male, female same, non-binary different","Female, non-binary same, male different", "All different"))) %>%
  filter(cond =="No gender differences")%>%
  select(ci_width_y, cond, estimate,reps, prop_resp_male, nb_representation,method,bias_y_gender_f,bias_y_gender_m,bias_y_gender_nb)%>%
  pivot_longer(cols = starts_with("bias_y_gender_"), 
               names_to = "gender",
               values_to = "bias_y", names_repair = "unique")%>%
  mutate(gender = fct_recode(gender,"Female" = "bias_y_gender_f","Male" = "bias_y_gender_m","Non-binary" = "bias_y_gender_nb"))%>%
  group_by(method, nb_representation, prop_resp_male, estimate,gender)%>%
  summarise(mean_bias = mean(bias_y,na.rm = TRUE), low025 = quantile(bias_y, .025,na.rm = TRUE), up975 = quantile(bias_y, .975,na.rm = TRUE))%>%
  ggplot(., aes(x=method, y = mean_bias, ymin =low025, ymax=up975, colour = gender, shape = nb_representation))+
  geom_point(position = position_dodge(.9))+
  geom_errorbar(width = 0,alpha = .3, position = position_dodge(.9))+
  facet_grid(prop_resp_male~estimate, scales = "free_x")+
  scale_colour_manual(values = c("#009E73","#D55E00","#56B4E9"))+# colours from the colorbling palette in ggthemes
  theme_bw()+
  coord_flip()+
  labs(shape = "Representation of non-binary individuals", colour = "gender")+
  theme(legend.position = "bottom",,
        axis.title.y = element_blank())+
  ylab("Estimate Bias")

bias_gender

ggsave("Appendix_Figures/mrp_wtd_gender_bias_nodiff.png",bias_gender, width = 20, height = 10, units = "cm")

```


Gender interval width

```{r}
ci_width_gender = results_biasvar %>%
  mutate(cond =  factor(cond, labels = c("No gender differences","Male, female same, non-binary different","Female, non-binary same, male different", "All different"))) %>%
  filter(cond =="No gender differences")%>%
  select( cond, estimate,reps, prop_resp_male, nb_representation,method,ci_width_y_gender_f,ci_width_y_gender_m,ci_width_y_gender_nb)%>%
  pivot_longer(cols = starts_with("ci_width_y_gender_"), 
               names_to = "gender",
               values_to = "ci_width_y", names_repair = "unique")%>%
  mutate(gender = fct_recode(gender,"Female" = "ci_width_y_gender_f","Male" = "ci_width_y_gender_m","Non-binary" = "ci_width_y_gender_nb"))%>%
  group_by(method, nb_representation, prop_resp_male, estimate,gender)%>%
  summarise(mean_ci_width = mean(ci_width_y,na.rm = TRUE), low025 = quantile(ci_width_y, .025,na.rm = TRUE), up975 = quantile(ci_width_y, .975,na.rm = TRUE))%>%
  ggplot(., aes(x=method, y = mean_ci_width, ymin =low025, ymax=up975, colour = gender, shape = nb_representation))+
  geom_point(position = position_dodge(.9))+
  geom_errorbar(width = 0,alpha = .3, position = position_dodge(.9))+
  facet_grid(prop_resp_male~estimate, scales = "free_x")+
  scale_colour_manual(values = c("#009E73","#D55E00","#56B4E9"))+# colours from the colorbling palette in ggthemes
  theme_bw()+
  coord_flip()+
  labs(shape = "Representation of non-binary individuals", colour = "gender")+
  theme(legend.position = "bottom",,
        axis.title.y = element_blank())+
  ylab("Estimate ci_width")

ci_width_gender

ggsave("Appendix_Figures/mrp_wtd_gender_ci_width_nodiff.png",ci_width_gender, width = 20, height = 10, units = "cm")

```



## Focussing on where non-binary folks have different experiences

We see that the response behaviour impacts the efficacy of using demographics.

Note that imputation error isn't included in uncertainty

```{r}
bias_pop = results_biasvar %>%
  mutate(cond =  factor(cond, labels = c("No gender differences","Male, female same, non-binary different","Female, non-binary same, male different", "All different"))) %>%
  filter(cond =="Male, female same, non-binary different")%>%
  select(bias_y, ci_width_y, cond, estimate,reps, prop_resp_male, nb_representation,method)%>%
  group_by(method, nb_representation, prop_resp_male, estimate)%>%
  summarise(mean_bias = mean(bias_y), low025 = quantile(bias_y, .025), up975 = quantile(bias_y, .975))%>%
  ggplot(., aes(x=method, y = mean_bias, ymin =low025, ymax=up975, colour = nb_representation))+
  geom_hline(yintercept=0)+
  geom_point(position = position_dodge(.5))+
  geom_errorbar(width = 0,alpha = .3, position = position_dodge(.5))+
  facet_grid(prop_resp_male~estimate)+
  ggthemes::scale_color_colorblind()+
  theme_bw()+
  coord_flip()+
  labs(colour = "Representation of non-binary individuals")+
  theme(legend.position = "bottom",,
        axis.title.y = element_blank())+
  ylab("Bias at estimating population mean")

bias_pop

ggsave("Appendix_Figures/mrp_wtd_y_bias_nbdiff.png",bias_pop, width = 20, height = 10, units = "cm")
```



```{r}
            
width_pop = results_biasvar %>%
  mutate(cond =  factor(cond, labels = c("No gender differences","Male, female same, non-binary different","Female, non-binary same, male different", "All different"))) %>%
  filter(cond =="Male, female same, non-binary different")%>%
  select(bias_y, ci_width_y, cond, estimate,reps, prop_resp_male, nb_representation,method)%>%
  group_by(method, nb_representation, prop_resp_male, estimate)%>%
  summarise(mean_width = mean(ci_width_y), low025 = quantile(ci_width_y, .025), up975 = quantile(ci_width_y, .975))%>%
  ggplot(., aes(x=method, y = mean_width, ymin =low025, ymax=up975, colour = nb_representation))+
  geom_point(position = position_dodge(.5))+
  geom_errorbar(width = 0,alpha = .3, position = position_dodge(.5))+
  facet_grid(prop_resp_male~estimate, scales = "free_x")+
  ggthemes::scale_color_colorblind()+
  theme_bw()+
  coord_flip()+
  labs(colour = "Representation of non-binary individuals")+
  theme(legend.position = "bottom",,
        axis.title.y = element_blank())+
  ylab("Width of uncertainty")

width_pop

ggsave("Appendix_Figures/mrp_wtd_y_width_nbdiff.png",width_pop, width = 20, height = 10, units = "cm")
```

### Focussing on sex sub group estimates

Sex bias in estimates

```{r}
bias_sex = results_biasvar %>%
  mutate(cond =  factor(cond, labels = c("No gender differences","Male, female same, non-binary different","Female, non-binary same, male different", "All different"))) %>%
  filter(cond =="Male, female same, non-binary different")%>%
  select(ci_width_y, cond, estimate,reps, prop_resp_male, nb_representation,method,bias_y_sex_f,bias_y_sex_m)%>%
  pivot_longer(cols = starts_with("bias_y_sex_"), 
               names_to = "sex",
               values_to = "bias_y", names_repair = "unique")%>%
  mutate(sex = fct_recode(sex,"Female" = "bias_y_sex_f","Male" = "bias_y_sex_m"))%>%
  group_by(method, nb_representation, prop_resp_male, estimate,sex)%>%
  summarise(mean_bias = mean(bias_y), low025 = quantile(bias_y, .025), up975 = quantile(bias_y, .975))%>%
  ggplot(., aes(x=method, y = mean_bias, ymin =low025, ymax=up975, colour = sex, shape = nb_representation))+
  geom_point(position = position_dodge(.8))+
  geom_errorbar(width = 0,alpha = .3, position = position_dodge(.8))+
  facet_grid(prop_resp_male~estimate, scales = "free_x")+
  scale_colour_manual(values = c("#009E73","#D55E00"))+# colours from the colorbling palette in ggthemes
  theme_bw()+
  coord_flip()+
  labs(shape = "Representation of non-binary individuals", colour = "Sex")+
  theme(legend.position = "bottom",,
        axis.title.y = element_blank())+
  ylab("Estimate Bias")

bias_sex

ggsave("Appendix_Figures/mrp_wtd_sex_bias_nbdiff.png",bias_sex, width = 20, height = 10, units = "cm")

```


Sex bias in estimates

```{r}
ciwidth_sex = results_biasvar %>%
  mutate(cond =  factor(cond, labels = c("No gender differences","Male, female same, non-binary different","Female, non-binary same, male different", "All different"))) %>%
  filter(cond =="Male, female same, non-binary different")%>%
  select(cond, estimate,reps, prop_resp_male, nb_representation,method,ci_width_y_sex_f,ci_width_y_sex_m)%>%
  pivot_longer(cols = starts_with("ci_width_y_sex_"), 
               names_to = "sex",
               values_to = "ciwidth_y", names_repair = "unique")%>%
  mutate(sex = fct_recode(sex,"Female" = "ci_width_y_sex_f","Male" = "ci_width_y_sex_m"))%>%
  group_by(method, nb_representation, prop_resp_male, estimate,sex)%>%
  summarise(ciwidth = mean(ciwidth_y), low025 = quantile(ciwidth_y, .025), up975 = quantile(ciwidth_y, .975))%>%
  ggplot(., aes(x=method, y = ciwidth, ymin =low025, ymax=up975, colour = sex, shape = nb_representation))+
  geom_point(position = position_dodge(.8))+
  geom_errorbar(width = 0,alpha = .3, position = position_dodge(.8))+
  facet_grid(prop_resp_male~estimate, scales = "free_x")+
  scale_colour_manual(values = c("#009E73","#D55E00"))+# colours from the colorbling palette in ggthemes
  theme_bw()+
  coord_flip()+
  labs(shape = "Representation of non-binary individuals", colour = "Sex")+
  theme(legend.position = "bottom",,
        axis.title.y = element_blank())+
  ylab("Width of uncertainty")

ciwidth_sex

ggsave("Appendix_Figures/mrp_wtd_sex_ciwidth_nbdiff.png",ciwidth_sex, width = 20, height = 10, units = "cm")

```


### Focussing on gender sub group estimates

gender bias in estimates

```{r}
bias_gender = results_biasvar %>%
  mutate(cond =  factor(cond, labels = c("No gender differences","Male, female same, non-binary different","Female, non-binary same, male different", "All different"))) %>%
  filter(cond =="Male, female same, non-binary different")%>%
  select(ci_width_y, cond, estimate,reps, prop_resp_male, nb_representation,method,bias_y_gender_f,bias_y_gender_m,bias_y_gender_nb)%>%
  pivot_longer(cols = starts_with("bias_y_gender_"), 
               names_to = "gender",
               values_to = "bias_y", names_repair = "unique")%>%
  mutate(gender = fct_recode(gender,"Female" = "bias_y_gender_f","Male" = "bias_y_gender_m","Non-binary" = "bias_y_gender_nb"))%>%
  group_by(method, nb_representation, prop_resp_male, estimate,gender)%>%
  summarise(mean_bias = mean(bias_y,na.rm = TRUE), low025 = quantile(bias_y, .025,na.rm = TRUE), up975 = quantile(bias_y, .975,na.rm = TRUE))%>%
  ggplot(., aes(x=method, y = mean_bias, ymin =low025, ymax=up975, colour = gender, shape = nb_representation))+
  geom_point(position = position_dodge(.9))+
  geom_errorbar(width = 0,alpha = .3, position = position_dodge(.9))+
  facet_grid(prop_resp_male~estimate, scales = "free_x")+
  scale_colour_manual(values = c("#009E73","#D55E00","#56B4E9"))+# colours from the colorbling palette in ggthemes
  theme_bw()+
  coord_flip()+
  labs(shape = "Representation of non-binary individuals", colour = "gender")+
  theme(legend.position = "bottom",,
        axis.title.y = element_blank())+
  ylab("Estimate Bias")

bias_gender

ggsave("Appendix_Figures/mrp_wtd_gender_bias_nbdiff.png",bias_gender, width = 20, height = 10, units = "cm")

```


Gender interval width

```{r}
ci_width_gender = results_biasvar %>%
  mutate(cond =  factor(cond, labels = c("No gender differences","Male, female same, non-binary different","Female, non-binary same, male different", "All different"))) %>%
  filter(cond =="Male, female same, non-binary different")%>%
  select( cond, estimate,reps, prop_resp_male, nb_representation,method,ci_width_y_gender_f,ci_width_y_gender_m,ci_width_y_gender_nb)%>%
  pivot_longer(cols = starts_with("ci_width_y_gender_"), 
               names_to = "gender",
               values_to = "ci_width_y", names_repair = "unique")%>%
  mutate(gender = fct_recode(gender,"Female" = "ci_width_y_gender_f","Male" = "ci_width_y_gender_m","Non-binary" = "ci_width_y_gender_nb"))%>%
  group_by(method, nb_representation, prop_resp_male, estimate,gender)%>%
  summarise(mean_ci_width = mean(ci_width_y,na.rm = TRUE), low025 = quantile(ci_width_y, .025,na.rm = TRUE), up975 = quantile(ci_width_y, .975,na.rm = TRUE))%>%
  ggplot(., aes(x=method, y = mean_ci_width, ymin =low025, ymax=up975, colour = gender, shape = nb_representation))+
  geom_point(position = position_dodge(.9))+
  geom_errorbar(width = 0,alpha = .3, position = position_dodge(.9))+
  facet_grid(prop_resp_male~estimate, scales = "free_x")+
  scale_colour_manual(values = c("#009E73","#D55E00","#56B4E9"))+# colours from the colorbling palette in ggthemes
  theme_bw()+
  coord_flip()+
  labs(shape = "Representation of non-binary individuals", colour = "gender")+
  theme(legend.position = "bottom",,
        axis.title.y = element_blank())+
  ylab("Estimate ci_width")

ci_width_gender

ggsave("Appendix_Figures/mrp_wtd_gender_ci_width_nbdiff.png",ci_width_gender, width = 20, height = 10, units = "cm")

```


## Focussing on where men have different experiences

We see that the response behaviour impacts the efficacy of using demographics.

Note that imputation error isn't included in uncertainty

```{r}
bias_pop = results_biasvar %>%
  mutate(cond =  factor(cond, labels = c("No gender differences","Male, female same, non-binary different","Female, non-binary same, male different", "All different"))) %>%
  filter(cond =="Female, non-binary same, male different")%>%
  select(bias_y, ci_width_y, cond, estimate,reps, prop_resp_male, nb_representation,method)%>%
  group_by(method, nb_representation, prop_resp_male, estimate)%>%
  summarise(mean_bias = mean(bias_y), low025 = quantile(bias_y, .025), up975 = quantile(bias_y, .975))%>%
  ggplot(., aes(x=method, y = mean_bias, ymin =low025, ymax=up975, colour = nb_representation))+
  geom_hline(yintercept=0)+
  geom_point(position = position_dodge(.5))+
  geom_errorbar(width = 0,alpha = .3, position = position_dodge(.5))+
  facet_grid(prop_resp_male~estimate)+
  ggthemes::scale_color_colorblind()+
  theme_bw()+
  coord_flip()+
  labs(colour = "Representation of non-binary individuals")+
  theme(legend.position = "bottom",,
        axis.title.y = element_blank())+
  ylab("Bias at estimating population mean")

bias_pop

ggsave("Appendix_Figures/mrp_wtd_y_bias_malediff.png",bias_pop, width = 20, height = 10, units = "cm")
```



```{r}
            
width_pop = results_biasvar %>%
  mutate(cond =  factor(cond, labels = c("No gender differences","Male, female same, non-binary different","Female, non-binary same, male different", "All different"))) %>%
  filter(cond =="Female, non-binary same, male different")%>%
  select(bias_y, ci_width_y, cond, estimate,reps, prop_resp_male, nb_representation,method)%>%
  group_by(method, nb_representation, prop_resp_male, estimate)%>%
  summarise(mean_width = mean(ci_width_y), low025 = quantile(ci_width_y, .025), up975 = quantile(ci_width_y, .975))%>%
  ggplot(., aes(x=method, y = mean_width, ymin =low025, ymax=up975, colour = nb_representation))+
  geom_point(position = position_dodge(.5))+
  geom_errorbar(width = 0,alpha = .3, position = position_dodge(.5))+
  facet_grid(prop_resp_male~estimate, scales = "free_x")+
  ggthemes::scale_color_colorblind()+
  theme_bw()+
  coord_flip()+
  labs(colour = "Representation of non-binary individuals")+
  theme(legend.position = "bottom",,
        axis.title.y = element_blank())+
  ylab("Width of uncertainty")

width_pop

ggsave("Appendix_Figures/mrp_wtd_y_width_malediff.png",width_pop, width = 20, height = 10, units = "cm")
```

### Focussing on sex sub group estimates

Sex bias in estimates

```{r}
bias_sex = results_biasvar %>%
  mutate(cond =  factor(cond, labels = c("No gender differences","Male, female same, non-binary different","Female, non-binary same, male different", "All different"))) %>%
  filter(cond =="Female, non-binary same, male different")%>%
  select(ci_width_y, cond, estimate,reps, prop_resp_male, nb_representation,method,bias_y_sex_f,bias_y_sex_m)%>%
  pivot_longer(cols = starts_with("bias_y_sex_"), 
               names_to = "sex",
               values_to = "bias_y", names_repair = "unique")%>%
  mutate(sex = fct_recode(sex,"Female" = "bias_y_sex_f","Male" = "bias_y_sex_m"))%>%
  group_by(method, nb_representation, prop_resp_male, estimate,sex)%>%
  summarise(mean_bias = mean(bias_y), low025 = quantile(bias_y, .025), up975 = quantile(bias_y, .975))%>%
  ggplot(., aes(x=method, y = mean_bias, ymin =low025, ymax=up975, colour = sex, shape = nb_representation))+
  geom_point(position = position_dodge(.8))+
  geom_errorbar(width = 0,alpha = .3, position = position_dodge(.8))+
  facet_grid(prop_resp_male~estimate, scales = "free_x")+
  scale_colour_manual(values = c("#009E73","#D55E00"))+# colours from the colorbling palette in ggthemes
  theme_bw()+
  coord_flip()+
  labs(shape = "Representation of non-binary individuals", colour = "Sex")+
  theme(legend.position = "bottom",,
        axis.title.y = element_blank())+
  ylab("Estimate Bias")

bias_sex

ggsave("Appendix_Figures/mrp_wtd_sex_bias_malediff.png",bias_sex, width = 20, height = 10, units = "cm")

```


Sex bias in estimates

```{r}
ciwidth_sex = results_biasvar %>%
  mutate(cond =  factor(cond, labels = c("No gender differences","Male, female same, non-binary different","Female, non-binary same, male different", "All different"))) %>%
  filter(cond =="Female, non-binary same, male different")%>%
  select(cond, estimate,reps, prop_resp_male, nb_representation,method,ci_width_y_sex_f,ci_width_y_sex_m)%>%
  pivot_longer(cols = starts_with("ci_width_y_sex_"), 
               names_to = "sex",
               values_to = "ciwidth_y", names_repair = "unique")%>%
  mutate(sex = fct_recode(sex,"Female" = "ci_width_y_sex_f","Male" = "ci_width_y_sex_m"))%>%
  group_by(method, nb_representation, prop_resp_male, estimate,sex)%>%
  summarise(ciwidth = mean(ciwidth_y), low025 = quantile(ciwidth_y, .025), up975 = quantile(ciwidth_y, .975))%>%
  ggplot(., aes(x=method, y = ciwidth, ymin =low025, ymax=up975, colour = sex, shape = nb_representation))+
  geom_point(position = position_dodge(.8))+
  geom_errorbar(width = 0,alpha = .3, position = position_dodge(.8))+
  facet_grid(prop_resp_male~estimate, scales = "free_x")+
  scale_colour_manual(values = c("#009E73","#D55E00"))+# colours from the colorbling palette in ggthemes
  theme_bw()+
  coord_flip()+
  labs(shape = "Representation of non-binary individuals", colour = "Sex")+
  theme(legend.position = "bottom",,
        axis.title.y = element_blank())+
  ylab("Width of uncertainty")

ciwidth_sex

ggsave("Appendix_Figures/mrp_wtd_sex_ciwidth_malediff.png",ciwidth_sex, width = 20, height = 10, units = "cm")

```


### Focussing on gender sub group estimates

gender bias in estimates

```{r}
bias_gender = results_biasvar %>%
  mutate(cond =  factor(cond, labels = c("No gender differences","Male, female same, non-binary different","Female, non-binary same, male different", "All different"))) %>%
  filter(cond =="Female, non-binary same, male different")%>%
  select(ci_width_y, cond, estimate,reps, prop_resp_male, nb_representation,method,bias_y_gender_f,bias_y_gender_m,bias_y_gender_nb)%>%
  pivot_longer(cols = starts_with("bias_y_gender_"), 
               names_to = "gender",
               values_to = "bias_y", names_repair = "unique")%>%
  mutate(gender = fct_recode(gender,"Female" = "bias_y_gender_f","Male" = "bias_y_gender_m","Non-binary" = "bias_y_gender_nb"))%>%
  group_by(method, nb_representation, prop_resp_male, estimate,gender)%>%
  summarise(mean_bias = mean(bias_y,na.rm = TRUE), low025 = quantile(bias_y, .025,na.rm = TRUE), up975 = quantile(bias_y, .975,na.rm = TRUE))%>%
  ggplot(., aes(x=method, y = mean_bias, ymin =low025, ymax=up975, colour = gender, shape = nb_representation))+
  geom_point(position = position_dodge(.9))+
  geom_errorbar(width = 0,alpha = .3, position = position_dodge(.9))+
  facet_grid(prop_resp_male~estimate, scales = "free_x")+
  scale_colour_manual(values = c("#009E73","#D55E00","#56B4E9"))+# colours from the colorbling palette in ggthemes
  theme_bw()+
  coord_flip()+
  labs(shape = "Representation of non-binary individuals", colour = "gender")+
  theme(legend.position = "bottom",,
        axis.title.y = element_blank())+
  ylab("Estimate Bias")

bias_gender

ggsave("Appendix_Figures/mrp_wtd_gender_bias_malediff.png",bias_gender, width = 20, height = 10, units = "cm")

```


Gender interval width

```{r}
ci_width_gender = results_biasvar %>%
  mutate(cond =  factor(cond, labels = c("No gender differences","Male, female same, non-binary different","Female, non-binary same, male different", "All different"))) %>%
  filter(cond =="Female, non-binary same, male different")%>%
  select( cond, estimate,reps, prop_resp_male, nb_representation,method,ci_width_y_gender_f,ci_width_y_gender_m,ci_width_y_gender_nb)%>%
  pivot_longer(cols = starts_with("ci_width_y_gender_"), 
               names_to = "gender",
               values_to = "ci_width_y", names_repair = "unique")%>%
  mutate(gender = fct_recode(gender,"Female" = "ci_width_y_gender_f","Male" = "ci_width_y_gender_m","Non-binary" = "ci_width_y_gender_nb"))%>%
  group_by(method, nb_representation, prop_resp_male, estimate,gender)%>%
  summarise(mean_ci_width = mean(ci_width_y,na.rm = TRUE), low025 = quantile(ci_width_y, .025,na.rm = TRUE), up975 = quantile(ci_width_y, .975,na.rm = TRUE))%>%
  ggplot(., aes(x=method, y = mean_ci_width, ymin =low025, ymax=up975, colour = gender, shape = nb_representation))+
  geom_point(position = position_dodge(.9))+
  geom_errorbar(width = 0,alpha = .3, position = position_dodge(.9))+
  facet_grid(prop_resp_male~estimate, scales = "free_x")+
  scale_colour_manual(values = c("#009E73","#D55E00","#56B4E9"))+# colours from the colorbling palette in ggthemes
  theme_bw()+
  coord_flip()+
  labs(shape = "Representation of non-binary individuals", colour = "gender")+
  theme(legend.position = "bottom",,
        axis.title.y = element_blank())+
  ylab("Estimate ci_width")

ci_width_gender

ggsave("Appendix_Figures/mrp_wtd_gender_ci_width_malediff.png",ci_width_gender, width = 20, height = 10, units = "cm")

```